---
title: "Making quick, interactive webpages with Rstudio"
author: "Matt Pocernich"
date: April 16, 2015
#output: ioslides_presentation
output:
  html_document:
    toc: true
    theme: cosmo
    highlight: espresso
    fig_width: 7
    fig_height: 6

---

## Background

For this talk, I will assume you have a bit of knowledge with the following.

- git and github
- RStudio
- R Markdown
- Interactive plots


## Using RStudio to provide a presentation or document template

* Templates now available for different purposes
* Provide a good starting point
* R Markdown is evolving and RStudio is now created a product called R Markdown V2


## googleVis - Motion Chart

```{r results = 'asis', echo=FALSE, warning=FALSE, message=FALSE, tidy = TRUE}

require(googleVis)
op <- options(gvis.plot.tag='chart')
M <- gvisMotionChart(Fruits, "Fruit", "Year", options=list(width=800, height=410))
plot(M)

```


## Leaflet

```{r results = 'asis', echo=FALSE, tidy=TRUE, warning=FALSE, message=FALSE}

library(leaflet)
location <- read.csv("MonitoringLocationsExport (1).csv")
#devtools::install_github("rstudio/leaflet")

library(leaflet)

m <-  leaflet() %>% addTiles()
 
m %>% setView(-107.03, 39.32, zoom = 10)%>% 
     addCircles(data=location) %>% 
      addMarkers(data=location, popup=location$Name )


```


## Datatable

```{r}
library(DT)
datatable(iris, filter = 'top',rownames = FALSE)

```

## Publish to web using Rpubs
* Rpubs is a service provided by Rstudio to share documents created using R Markdown.
* Code is not shared
* By design, everything is public
* Very easy using menu option in RStudio.

## Creating a web page using github.

1.  Locally, create Rmd or Rpres document
2.  Save as html document
3.  Commit locally and push to project directory ( assuming one has already been created.)
4.  Branch called 'gh-pages' of master directory in github 
5.  Add .nojekll file
6.  Web page is create.

## Command line steps (Goto Git tab > More > Shell)

1. git branch gh-pages
2. git checkout gh-pages
3. git push origin gh-pages
4. touch .nojekll
5. git add .nojekll
6. git commit -a -m "Initial commit"
7. git push origin gh-pages

## Gaining better control

* Changing Presentation Style
* Changing Font Sizes

## Random Findings

* Some images such as googleVis plots won't render unless saved and viewed in an html document.
* Update to the most recent version of RStudio.  I encountered an error in using Rpubs that required I updatem to RStudio.

